The COVID-19 Pandemic's Impact on Bullying Search Intensity with respect to Asian Population

### 2023-02-22 Outputs/Paper/paper.qmd
Retouched introduction

---
title: "The COVID-19 Pandemic's Impact on Bullying Search Intensity with respect to Asian Population"
author: 
  - Will Davidson
  - Jason Ngo
  - Annie Yan
thanks: "Code and data are available at: https://github.com/AnnieYan0807/Analysis-on-The-COVID-19-Pandemic-Disrupted-Both-School-Bullying-and-Cyberbullying. The replication on the SSRP can be found at : https://doi.org/10.48152/ssrp-54f4-p919"
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
format: 
  pdf:
    documentclass: article
    geometry: margin = 1in
    abstract: "The Covid-19 pandemic incited a wave of anti-Asian hate crimes across the United States including derogatory language in the media, random bullying, and violent, senseless murders. This paper analyzes how high school closures and the shift to online learning by schools throughout the pandemic, impacted incidents of bullying of Asian students compared to non Asian students when compared to pre-pandemic trends and in-person learning. Results suggest that while the overall trend in bullying of high school students has been in decline across all states between 2016-2021, with a larger drop during Covid-19, the states with high Asian populations saw greater incidents of bullying when compared to states with low Asian populations over the six year period. These findings tell both a good news story of declining bullying trends in the US school system and a highly concerning narrative that anti-Asian bullying is not a result of Covid-19, but rather an intensified awareness of pre-existing racism."
number-sections: true
bibliography: references.bib
---

@@

It has been widely reported in the media that discrimination and overt anti-Asian racism due to the COVID-19 pandemic is on the rise. By contrast, Andrew Bacher-Hicks, The COVID-19 Pandemic Disrupted Both School Bullying and Cyberbullying, illustrates how the rate of bullying incidents among high schools declined during the pandemic, and discussed how these learnings can be helpful in further reducing bullying with targetted prevention and intervention strategies (Bacher-Hicks, 2020). Their analysis uses data from Google trends on search intensity for bullying related terms; cyberbullying, school bullying and bullying, and the times of the year bullying occurs. Their research proved that search intensity for bullying related terms, and state self-reported bullying rates are strongly correlated.

This paper will use the initial analysis from Bachman-Hicks research to expand on their general findings to determine if anti-Asian bullying, more specifically, has followed the same overall declining trend among high school students across America.  We will conduct our own detailed data analysis and interpretation of their results and then design three different reproductions of their data. First, we will examine all bullying, cyberbullying, and school bullying searches in the Top 10 Asian populated states and discuss how bullying rates changed from the pre-pandemic to post pandemic. Second, we will look at the top 10 Asian populated states' frequency of school bullying searches compared to the searches across the entire nation. Finally, we will examine the same searches in the top 10 lowest Asian populated states to gain a better understanding of how the lowest Asian populated states relate to the highest in terms of bullying search intensity.

In this document, we will show that while rates of bullying have declined during the Covid-19 pandemic among high school students, they have declined less in schools located in states where people of Asian descent are the highest.

@@

The top 10 Asian population states experienced more school and cyber bullying than the bottom 10 Asian population states. From (@cit7), there has been a 70% increase in Asian American cyberbullying in 2020. Anti-Asian xenophobia fueled by Covid-19 has led to an increase of hate towards Asian-Americans. With this in mind, Asian population does correlate with respect to the disparity between bullying searches from the top 10 Asian population states with bullying searches from the bottom 10 Asian population states.

>>>>

---
title: "The COVID-19 Pandemic's Impact on Bullying Search Intensity with respect to Asian Population"
author: 
  - Will Davidson
  - Jason Ngo
  - Annie Yan
thanks: "Code and data are available at: https://github.com/AnnieYan0807/Analysis-on-The-COVID-19-Pandemic-Disrupted-Both-School-Bullying-and-Cyberbullying. The replication on the SSRP can be found at : https://doi.org/10.48152/ssrp-54f4-p919"
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
format: 
  pdf:
    documentclass: article
    geometry: margin = 1in
    abstract: "The COVID-19 pandemic incited a wave of anti-Asian hate crimes across the United States including derogatory language in the media, random bullying, and violent, senseless murders. This paper analyzes how high school closures and the shift to online learning by schools throughout the pandemic, impacted incidents of bullying of Asian students compared to non Asian students when compared to pre-pandemic trends and in-person learning. Results suggest that while the overall trend in bullying of high school students has been in decline across all states between 2016-2021, with a larger drop during COVID-19, the states with high Asian populations saw greater incidents of bullying when compared to states with low Asian populations over the six year period. These findings tell both a good news story of declining bullying trends in the US school system and a highly concerning narrative that anti-Asian bullying is not a result of COVID-19, but rather an intensified awareness of pre-existing racism."
number-sections: true
bibliography: references.bib
---

@@

It has been widely reported in the media that discrimination and overt anti-Asian racism due to the COVID-19 pandemic is on the rise. The paper 'The COVID-19 Pandemic Disrupted Both School Bullying and Cyberbullying' (@cit4) illustrated how bullying incidents among high schools nationwide declined during the pandemic, and discussed how those findings could be helpful in further reducing bullying with targeted prevention and intervention strategies. Their analysis used data from Google Trends on search intensity for bullying related terms; cyberbullying, school bullying and bullying, and the times of the year bullying occurs. Their research proved that search intensity for bullying related terms, and state self-reported bullying rates are strongly correlated.

This paper will expand upon the initial analysis from the aforementioned paper to determine if, more specifically, anti-Asian bullying has followed the same declining trend among high school students across America and if the COVID-19 pandemic has affected that trend.  We will conduct our own detailed data analysis and interpretation of their results and then design three different reproductions of their data. First, we will examine all bullying, cyberbullying, and school bullying searches in the Top 10 Asian populated states and discuss how bullying rates changed from the pre-pandemic to post pandemic. Second, we will look at the top 10 Asian populated states' frequency of school bullying searches compared to the searches across the entire nation. Finally, we will examine the same searches in the top 10 lowest Asian populated states to gain a better understanding of how the lowest Asian populated states relate to the highest in terms of bullying search intensity.

Our findings will show while rates of bullying have declined during the COVID-19 pandemic among high school students, they have declined less in schools located in states where people of Asian descent are the highest.

@@

The top 10 Asian population states experienced more school and cyber bullying than the bottom 10 Asian population states. From (@cit7), there has been a 70% increase in Asian American cyberbullying in 2020. Anti-Asian xenophobia fueled by COVID-19 has led to an increase of hate towards Asian-Americans. With this in mind, Asian population does correlate with respect to the disparity between bullying searches from the top 10 Asian population states with bullying searches from the bottom 10 Asian population states.
